Transfer of Learned Opponent Models in Zero Sum Games

### 2020-01-21 Experiment_2/Experiment_2_modelling.Rmd
changes ToM comp model

```{r}
# Assumes within game transfer of opponent model between stages, but boolena for between game transfer. 
exp2_naive_bayes <- function(par,data,opp_strategy_vec,return_value,btwn_transfer) {

@@

      ## KEY CODE FOR LEARNING TRANSFER !! (if no OM transfer reset prior to uniform)#####
      # Round 1 of stage 1 
      if (data[t,"stage"] == 1) {
        if (!(btwn_transfer)){
          opp_prior_vec <- rep(1/num_strat, num_strat)
        } else { # <- TRANFER 
          # if there is between game transfer, then the opp_prior_vec should store what was learned about the SECOND opponent 
          # ...from stage 4 of previous game (or uniform if it is first game of RPS). store that before proceeding
          opp2_prior_vec <- opp_prior_vec
          # if between game transfer use stored opp1 prior vector from previous game (or uniform if first game  RPS) 
          opp_prior_vec <- opp1_prior_vec
        }

      # we are round 1 of stage 2, keep opp vector from round 20 of stage 1  for stage 3
      } else if (data[t,"stage"] == 2) {
          # hold the probs vector of Opp type learned in stage 1 in memory and save to temp.
          opp1_prior_temp <- opp_prior_vec
          # If no between games transfer reset prior to uniform 
          if (!(btwn_transfer)){
            opp_prior_vec <- rep(1/num_strat, num_strat)
            } else {
              opp_prior_vec <- opp2_prior_vec
            }

      # we are round 1 of stage 3, use vector learned from stage 1, keep opp vector from round 20 of stage 2 for stage 4
      } else if (data[t,"stage"] == 3) { 
        opp2_prior_temp <- opp_prior_vec
        opp_prior_vec <- opp1_prior_temp

      # We are in round 1 of stage 4,
      }  else if (data[t,"stage"] == 4) {
        # Store what was learned about opponent 1 for nxt game...
        opp1_prior_vec <- opp_prior_vec
        # Use what was learned about opponent 2 from stage 2.
        opp_prior_vec <- opp2_prior_temp
      }

@@

      # Get which opponent strategy human current actn maps to (if index = 0 then human current action is br to level-0 comp_strat...)
      indices <- which(grepl(as.character(data[t,"h_action"]),br_hum,fixed = TRUE))

@@

exp2_naive_bayes(c(0.5,0.1),test_data,c("level0","level1","level2"),"-2loglik",TRUE)
```
## Fitting Bayesian model with transfer  
```{r}
exp2_TR_bayes <- list()
for(id in unique(dat_exp2$human_id)) {
  exp2_TR_bayes[[id]] <- list()
  tdat <- subset(dat_exp2,human_id == id)

@@

  exp2_TR_bayes[[id]] <- optim(c(0.1,0.1),fn=exp2_naive_bayes,gr = NULL, data=tdat,opp_strategy_vec = c("level0","level1","level2"),return_value = "-2loglik", btwn_transfer = TRUE,lower = c(0.01,0.01), upper = c(0.99,0.99), method="L-BFGS-B")
}
save(exp2_TR_bayes, file="exp2_TR_bayes.RData")

@@

## Fitting Bayesian model with NO trnsfer 
```{r}

exp2_NT_bayes <- list()
for(id in unique(dat_exp2$human_id)) {
  exp2_NT_bayes[[id]] <- list()
  tdat <- subset(dat_exp2,human_id == id)

  # exp2_NT_bayes[[id]] <- DEoptim(fn=naive_bayes, lower = c(0.0,0.0), upper = c(1.0,1.0), data=tdat, opp_strategy_vec = c("level0","level1","level2"),return_value = "-2loglik", opp_mod_transfer = FALSE, control=list(trace = FALSE, parallelType=0,parVar = c("best_response")))

  exp2_NT_bayes[[id]] <- optim(c(0.1,0.1),fn=exp2_naive_bayes,gr = NULL, data=tdat,opp_strategy_vec = c("level0","level1","level2"),return_value = "-2loglik", opp_mod_transfer = FALSE, lower = c(0.01,0.01), upper = c(0.99,0.99), method="L-BFGS-B")
}

save(exp2_NT_bayes,file="exp2_NT_bayes.RData")
```

@@

load("exp2_TR_bayes.RData")
load("exp2_NT_bayes.RData")
load("exp2_QLS_modelling.RData")
load("exp2_SEWA_modelling.RData")
load("MBM2_modelling.RData")

@@

                         # Bayesian updating with/without transfer
                         "Bayes_Tr_BIC" = exp2_TR_bayes[[id]]$value + 2*log(180),
                         "Bayes_No_Tr_BIC" = exp2_NT_bayes[[id]]$value+ 2*log(180),
                         # Theta is the parameter governing AI stochasticity. Truth is 0.9
                         "theta_transfer" = exp2_TR_bayes[[id]]$par[1],
                         "theta_no_transfer" = exp2_NT_bayes[[id]]$par[1],
                         # Epsilone is parameter showing cases where human deviates from predictions about opponent (lower better)
                         "eps_transfer" = exp2_TR_bayes[[id]]$par[2],
                         "eps_no_transfer" = exp2_NT_bayes[[id]]$par[2],

@@

```{r}
exp2_table_results <- table(exp2_results[, "condition"],c("random","Bayes Tr","Bayes No Tr", "QL_states","S_EWA","MBM")[apply(exp2_results[,c("Random_BIC","Bayes_Tr_BIC","Bayes_No_Tr_BIC","QL_states_BIC","EWA_self_BIC","MBM2_BIC")],1,which.min)])

@@

```{r}
exp2_model_comp <- data.frame()
for(id in unique(dat_exp2$human_id)) {
  tdat <- subset(dat_exp2,human_id == id)
  tot_score <- sum(tdat$score)
  tot_time <- sum(tdat$human_rt)
  early_dat <- subset(tdat,between(tdat$round,2,6) & (game =="fwg"))
  #early_dat <- subset(tdat,between(tdat$round,2,6) & (game =="fwg" | game =="numbers") )
  tr_score <- sum(early_dat$score)
  id_results <- subset(exp2_results, ID == id)
  min_BIC <- apply(id_results[,c("Random_BIC","Bayes_Tr_BIC","Bayes_No_Tr_BIC","QL_states_BIC","EWA_self_BIC","MBM2_BIC")],1,min)

  best_model <- c("random","Bayes Tr","Bayes NT", "QL_states","S_EWA", "MBM")[apply(id_results[,c("Random_BIC","Bayes_Tr_BIC","Bayes_No_Tr_BIC","QL_states_BIC","EWA_self_BIC","MBM2_BIC")],1,which.min)]
  # 
 exp2_model_comp <- rbind(exp2_model_comp ,
                       data.frame(
                         "human_id" = id,
                         "condition" = dat_exp2[dat_exp2$human_id==id,"condition"][1],
                         "Early_game_score" = tr_score,
                         "Total_score" = tot_score,
                         "Best_model" = best_model,
                         "Total_time" = sum(tdat$human_rt),
                         "TR_minus_NT_BIC" = id_results[,"Bayes_Tr_BIC"] - id_results[,"Bayes_No_Tr_BIC"],
                         "Rand_minus_best_BIC" =  id_results[,"Random_BIC"] - min_BIC

>>>>

```{r}
# Assumes within game transfer of opponent model between stages, but boolena for between game transfer. 
TOM_model <- function(par, data, opp_strategy_vec, return_value, within_transfer, btwn_transfer) {

@@

      ## KEY CODE FOR LEARNING TRANSFER !! (if no OM transfer reset prior to uniform)#####
      # Round 1 of stage 1 
      if (data[t,"stage"] == 1) {
        if (btwn_transfer){
          # if there is between game transfer, then the opp_prior_vec should have stored what was learned about the SECOND opponent 
          # ...from stage 4 of previous game (or uniform if it is first game of RPS). store that before proceeding
          opp2_prior_vec <- opp_prior_vec
          # if between game transfer use stored opp1 prior vector from previous game (or uniform if first game  RPS) 
          opp_prior_vec <- opp1_prior_vec

        } else { # <- No between game TRANSFER 
          opp_prior_vec <- rep(1/num_strat, num_strat)
        }

      # we are round 1 of stage 2, keep opp vector from round 20 of stage 1  for stage 3
      } else if (data[t,"stage"] == 2) {
        if (within_transfer){
          # hold the probs vector of Opp type learned in stage 1 in memory and save to temp.
          opp1_prior_temp <- opp_prior_vec
          if (btwn_transfer){
            # If  between games transfer get prior from opp2 prior saved from last stage of last game 
            opp_prior_vec <- opp2_prior_vec
          } else { # if no between transfer start of first interaction with secnd opp should be reset
            opp_prior_vec <- rep(1/num_strat, num_strat)
          }

        } else { # Assume no between game transfer if no within. reasonable. 
          opp_prior_vec <- rep(1/num_strat, num_strat)    
        }

      # we are round 1 of stage 3
      } else if (data[t,"stage"] == 3) {
        if (within_transfer) {
          # if within_transfer keep opp vector from round 20 of stage 2 for stage 4
          opp2_prior_temp <- opp_prior_vec
          # if within_transfer, use what we learned about opp1 in stage 1 as new prior.  
          opp_prior_vec <- opp1_prior_temp

        } else { # No within transfer, dont store anything and reset priors
          opp_prior_vec <- rep(1/num_strat, num_strat)    
        }

      # We are in round 1 of stage 4,
      }  else if (data[t,"stage"] == 4) {
        if (within_transfer) {
          # Use what was learned about opponent 2 from stage 2.
          opp_prior_vec <- opp2_prior_temp
          if (btwn_transfer) {
            # Store what was learned about opponent 1 for nxt game...
           opp1_prior_vec <- opp_prior_vec
          }

        } else {
          opp_prior_vec <- rep(1/num_strat, num_strat)
        }

@@

      # Get which opponent strategy human current actn maps to (i.e, if index = 0 then human current action is best response to level-0 comp_strat...)
      indices <- which(grepl(as.character(data[t,"h_action"]),br_hum,fixed = TRUE))

@@

TOM_model(c(0.5,0.1),test_data,c("level0","level1","level2"),"-2loglik", within_transfer = TRUE, btwn_transfer = TRUE)
```
## Fitting Bayesian model with between game transfer (as well as within)  
```{r}
exp2_BT <- list()
for(id in unique(dat_exp2$human_id)) {
  exp2_BT[[id]] <- list()
  tdat <- subset(dat_exp2,human_id == id)

@@

  exp2_BT[[id]] <- optim(c(0.1,0.1),fn=TOM_model,gr = NULL, data=tdat,opp_strategy_vec = c("level0","level1","level2"),return_value = "-2loglik", within_transfer = TRUE, btwn_transfer = TRUE,lower = c(0.01,0.01), upper = c(0.99,0.99), method="L-BFGS-B")
}
save(exp2_BT, file="exp2_BT.RData")

@@

## Fitting ToM model with NO Between transfer (but with transfer within games)
```{r}

exp2_NO_BT <- list()
for(id in unique(dat_exp2$human_id)) {
  exp2_NO_BT[[id]] <- list()
  tdat <- subset(dat_exp2,human_id == id)

  # exp2_NO_BT[[id]] <- DEoptim(fn=naive_bayes, lower = c(0.0,0.0), upper = c(1.0,1.0), data=tdat, opp_strategy_vec = c("level0","level1","level2"),return_value = "-2loglik", opp_mod_transfer = FALSE, control=list(trace = FALSE, parallelType=0,parVar = c("best_response")))

  exp2_NO_BT[[id]] <- optim(c(0.1,0.1),fn=TOM_model,gr = NULL, data=tdat,opp_strategy_vec = c("level0","level1","level2"),return_value = "-2loglik", within_transfer = TRUE, btwn_transfer = FALSE, lower = c(0.01,0.01), upper = c(0.99,0.99), method="L-BFGS-B")
}

save(exp2_NO_BT,file="exp2_NO_BT.RData")
```

## Fitting Bayesian model with NO Between or within transfer
```{r}

exp2_NO_Tr <- list()
for(id in unique(dat_exp2$human_id)) {
  exp2_NO_Tr[[id]] <- list()
  tdat <- subset(dat_exp2,human_id == id)

  # exp2_NO_Tr[[id]] <- DEoptim(fn=naive_bayes, lower = c(0.0,0.0), upper = c(1.0,1.0), data=tdat, opp_strategy_vec = c("level0","level1","level2"),return_value = "-2loglik", opp_mod_transfer = FALSE, control=list(trace = FALSE, parallelType=0,parVar = c("best_response")))

  exp2_NO_Tr[[id]] <- optim(c(0.1,0.1),fn=TOM_model,gr = NULL, data=tdat,opp_strategy_vec = c("level0","level1","level2"),return_value = "-2loglik", within_transfer = FALSE , btwn_transfer = FALSE, lower = c(0.01,0.01), upper = c(0.99,0.99), method="L-BFGS-B")
}

save(exp2_NO_Tr,file="exp2_NO_Tr.RData")
```

@@

load("exp2_BT.RData")
load("exp2_NO_BT.RData")
load("exp2_QLS_modelling.RData")
load("exp2_SEWA_modelling.RData")
load("MBM2_modelling.RData")

@@

                         # Bayesian updating with/without transfer
                         "Btwn_TR_BIC" = exp2_BT[[id]]$value + 2*log(180),
                         "No_Btwn_Tr_BIC" = exp2_NO_BT[[id]]$value+ 2*log(180),
                         # Theta is the parameter governing AI stochasticity. Truth is 0.9
                         "theta_transfer" = exp2_BT[[id]]$par[1],
                         "theta_no_btw_tr" = exp2_NO_BT[[id]]$par[1],
                         # Epsilone is parameter showing cases where human deviates from predictions about opponent (lower better)
                         "eps_transfer" = exp2_BT[[id]]$par[2],
                         "eps_no_btwn_tr" = exp2_NO_BT[[id]]$par[2],

@@

```{r}
exp2_table_results <- table(exp2_results[, "condition"],c("random","Bayes Tr","Bayes No Tr", "QL_states","S_EWA","MBM")[apply(exp2_results[,c("Random_BIC","Btwn_TR_BIC","No_Btwn_Tr_BIC","QL_states_BIC","EWA_self_BIC","MBM2_BIC")],1,which.min)])

@@

```{r}
exp2_model_comp <- data.frame()
for(id in unique(dat_exp2$human_id)) {
  tdat <- subset(dat_exp2,human_id == id)
  tot_score <- sum(tdat$score)
  tot_time <- sum(tdat$human_rt)
  early_dat <- subset(tdat,between(tdat$round,2,6) & (game =="fwg"))
  #early_dat <- subset(tdat,between(tdat$round,2,6) & (game =="fwg" | game =="numbers") )
  tr_score <- sum(early_dat$score)
  id_results <- subset(exp2_results, ID == id)
  min_BIC <- apply(id_results[,c("Random_BIC","Btwn_TR_BIC","No_Btwn_Tr_BIC","QL_states_BIC","EWA_self_BIC","MBM2_BIC")],1,min)

  best_model <- c("random","ToM_BT","ToM_NBT", "QL_states","S_EWA", "MBM")[apply(id_results[,c("Random_BIC","Btwn_TR_BIC","No_Btwn_Tr_BIC","QL_states_BIC","EWA_self_BIC","MBM2_BIC")],1,which.min)]
  # 
 exp2_model_comp <- rbind(exp2_model_comp ,
                       data.frame(
                         "human_id" = id,
                         "condition" = dat_exp2[dat_exp2$human_id==id,"condition"][1],
                         "Early_game_score" = tr_score,
                         "Total_score" = tot_score,
                         "Best_model" = best_model,
                         "Total_time" = sum(tdat$human_rt),
                         "TR_minus_NT_BIC" = id_results[,"Btwn_TR_BIC"] - id_results[,"No_Btwn_Tr_BIC"],
                         "Rand_minus_best_BIC" =  id_results[,"Random_BIC"] - min_BIC

### 2020-01-21 Report/draft_report_v1.Rmd
changes ToM comp model

# Introduction
Being able to transfer previously acquired knowledge to a new domain is one of the hallmarks of human intelligence (Taylor, 2008) . Humans are naturally endowed with the ability to extract relevant features from a situation, identify the presence of these features in a novel setting and use previously acquired knowledge to adapt to previously unseen challenges using acquired knowledge. More formally, Perkins (1992) defines transfer of learning as the application of skills, knowledge, and/or attitudes that were learned in one situation to another learning situation. This typically human skill has so far eluded modern AI agents. Deep neural networks for instance can do very well on image recognition tasks and can even reach super-human performance levels on video and strategic board games. Yet they struggle to learn as fast or as efficiently as humans do, and more importantly they have a very limited ability to generalize and transfer knowledge to new domains. @lake2017building argue that human learning transfer abilities take advantage of important cognitive building blocks such as an abstract representation of concepts underlying tasks and compositionally structured causal models of the environment.

@@

In order to explore learning transfer in strategic settings, it is generally useful to study simple games as a model of more complex interactions. More specifically, we need a framework that allows the study of whether and how a player takes into consideration, over time, the impact of its current and future actions on the future actions of the opponent and the future cumulative rewards. Repeated games, in which players interact repeatedly with the same opponent and have the ability to learn about the opponent's strategies and preferences (Mertens, 1990) are particularly adapted to modelling learning about the opponent.

@@

To gain more insight into how participants played the games against the computer opponents, we compared multiple models of strategies the players may have been using to learn how to beat the opponent.  As a base model, we assume play is random, and each potential action is chosen with equal probability. Note that this corresponds to the Nash equilibrium strategy. Next, we include for comparison purposes a few other basic models of behavior, such as Q-learning on action choices, as well as a more sophisticatd Q-learning model incorporating a state space consisting of last round play. The Bayesian approach is represented by models whereby agents would update an initial belief over the opponent's strategy consisting of various level-k strategies (resp. 0,1 and 2). We fitted two models in which agents best respond to the opponent model. In the first, the beliefs about the opponent's adopted strategy are transfered across games, and another in which no transfer of opponent models is allowed.

Next, we fitted a self-tuning EWA model (Ho et al., 2004) both on action choices without states and with states consisting of lat round play. The self-tuning EWA model generalizes both reinforcement learning as well as fictitious play models and has been proven to do well than equilibrium models in various game situations. Finally, we also included a model-based reinforcement learning approach. whereby the agent learns the transition probabilities between states ans uses that to choose the best action, given the current state and it's belief about what the new state will be.

>>>>

# Introduction
Being able to transfer previously acquired knowledge to a new domain is one of the hallmarks of human intelligence. Humans are naturally endowed with the ability to extract relevant features from a situation, identify the presence of these features in a novel setting and use previously acquired knowledge to adapt to previously unseen challenges using acquired knowledge. More formally, Perkins (1992) defines transfer of learning as the application of skills, knowledge, and/or attitudes that were learned in one situation to another learning situation. This typically human skill has so far eluded modern AI agents. Deep neural networks for instance can do very well on image recognition tasks and can even reach super-human performance levels on video and strategic board games. Yet they struggle to learn as fast or as efficiently as humans do, and more importantly they have a very limited ability to generalize and transfer knowledge to new domains. @lake2017building argue that human learning transfer abilities take advantage of important cognitive building blocks such as an abstract representation of concepts underlying tasks and compositionally structured causal models of the environment.

@@

In order to explore learning transfer in strategic settings, it is generally useful to study simple games as a model of more complex interactions. More specifically, we need a framework that allows the study of whether and how a player takes into consideration, over time, the impact of its current and future actions on the future actions of the opponent and the future cumulative rewards. Repeated games, in which players interact repeatedly with the same opponent and have the ability to learn about the opponent's strategies and preferences (Mertens, 1990) are particularly adapted to the task of opponent modelling.

@@

To gain more insight into how participants played the games against the computer opponents, we compared multiple models of strategies the players may have been using to learn how to beat the opponent.  As a base model, we assume play is random, and each potential action is chosen with equal probability. Note that this corresponds to the Nash equilibrium strategy.

Next, we include for comparison purposes a simple model-free reinforcement learning algorithm, that reinforces actions that have led to positive rewards, and conversely lowers the likelihood of choosing actions that led to a negative reward, irrespective of any state. We will use a simple temporal difference learning update rule:

$$ V_{t+1}(a) = V_{t}(a) + \alpha*( R_{t}  - V_{t}(a)) $$

Where $ V_{t}(a) $ is the vlue associated with action $a$ at time $t$, $\alpha$ is the learning rate and $R_{t}$ the reward at time t. Actions are chosen based on action values using a softmax choice rule.

We extend this very simple model by adding a state space that consists of last round human and agent play. This is akin to using a Q-learning algorithm [@watkins1992q]. The update rule becomes:

$$ Q^{new}(s_{t},a_{t}) = Q(s_{t},a_{t}) + \alpha*( R_{t}  + \gamma*\underset{a}{\max}Q(s_{t+1},a) - Q(s_{t},a_{t}) ) $$

Where $Q(s_{t},a_{t})$ is the value of taking action $a$ when in state $s$ at time $t$,  $\gamma$ is the discount rate applied to future rewards. For instance, $Q(RS,P)$ denotes the value of taking action "Paper" this round if the player's last action was "Rock" and the opponent played "Scissors". This is a much richer model allowing the players to compute the values of actions conditional on past play.

### EWA Models 
Next, we use a self-tuning Experience Weighted attraction model [@ho2004economics]. EWA models are  model of behavior in repeated games, that nest two seemingly different approaches, namely reinforcement learning and belief learning. Belief based models are based on the assumption that players keep track of the frequency of past plays and best respond to that. In contrast, reinforcement learning does not take into account beliefs about other players, but is such that an action followed by a positive reward is more likely to be repeated than an action followed by a negative reward. The self-tunign EWA model has been shown to perform better than both these nested models in multiple repeated gmes and has the advantage of having only one free parameter, the inverse temperature in the softmax choice function.

Lt's define some notation in order to write the pdate rule of the self-tuning EWA model. For player i, there are $m_{i}$ strategies, denoted $s_{i}^{j}$ (i.e player i's strategy number j). Strategies actually played by i in period t, are denoted $s_{i}(t)$, while the opponent's strategy at time t is denoted $s_{-i}(t)$. After playing  $s_{i}^{j}$ at time $t$, player i payoff is denoted $\pi_{i}(s_{i}^{j},s_{-i}(t))$, and the actual payoff the player received is $\pi_{i}(t)$.

The EWA model is based on updating "Attractions" for each action over time. For instance, the attraction of strategy $j$ to player $i$ at time $t$ is written $A_{i}^{j}(t)$. Future action choice probabilities are based on these attractions using the softmax playing rule:

$$P_{i}^{j}(t+1) = \frac{e^{\lambda . A_{i}^{j}(t)}}{\sum_{k=1}^{m_{i}}e^{\lambda . A_{i}^{k}(t)}} $$

The attractions are updated over every time step $t$ using the followng update rule :

$$ A_{i}^{j}(t) =  \frac{\phi . N(t-1) . A_{i}^{j}(t-1) + [ \delta + (1-\delta) . I(s_{i}^{j},s_{i}(t))] . \pi_{i}(s_{i}^{j},s_{-i}(t)) } {\phi . N(t-1) + 1} $$

Here, I(x,y) is the indicator function equla to 1 if $ x = y$ and 0 otherwise. A simple way to think about this update rule is that attractions are multipled by a parameter that represents experince ($N(t-1)$) which is itself decaying by a wight $\phi$. The result is added to either the payoff received (when the indicator function is 0), or to $\delta$ times the foregone payoff (when indicator function is 1).   We can see that setting $\delta = 0$ leads to reinforcement of past actions, while positive and high delta parameters make the update rule take into account foregone payoffs, which is similar to weighted fictitous play [@cheung1994learning]. 
While the assumption in expanding the update rule above is that $\phi$ and $\delta$ are free parameters [@camerer1997experience], the self-tuning aspect of the model comes from the fact that these are now self-tuned using the formulas expanded in [@ho2004economics].

### ToM models

In this set of models, we assume that participants have a belief that the opponent is a level-k agent, with uniform probability of the level k, and use evidence of past play to update their beliefs in a Bayesian way about the true value of k. We use values of k  in ${0,1,2}$. We distinguish between multiple ToM models based on their ability to keep what was learned about the opponent in memory and hence facilitate transfer. In a No-Between-Transfer (NBT) model, players have no memory of what was learned about the opponent and start every new game assuming each level-k has equal probability. In the context of Experiment 2 where players face both opponents, this model assumes that participants transfer learning within the same game, from the first to the second intraction with the opponent, but are not able to transfer that learning to new games.

Conversely, In a Between-Transfer model (BT), players are assumed to keep in memory what was learned about the type of opponent faced (vector of probabilities of level-k) and use that at the beginning of each new game. In the context of experiment 2, we still assume that within game transfer is still present (from first to second interaction).

In experiment two, on top of these two models, we fit two other models: One in which we assume that players don't distinguish between the two opponents faced, so the opponent model vector is never updated (Naive). And finally, we also fit a model in which all stages of the game and all new games start with a fresh uniforme probability of level-k opponent (NT), so no within or between opponent model learning transfer.

In summary, we fit two ToM models for experiment 1-play ( NBT and BT), and 4 ToM models for experiment 2 ( NBT, BT, NT and Naive)

#############################################################
The Bayesian approach is represented by models whereby agents would update an initial belief over the opponent's strategy consisting of various level-k strategies (resp. 0,1 and 2). We fitted two models in which agents best respond to the opponent model. In the first, the beliefs about the opponent's adopted strategy are transfered across games, and another in which no transfer of opponent models is allowed.

Next, we fitted a self-tuning EWA model [@ho2004economics] both on action choices without states and with states consisting of lat round play. The self-tuning EWA model generalizes both reinforcement learning as well as fictitious play models and has been proven to do well than equilibrium models in various game situations. Finally, we also included a model-based reinforcement learning approach. whereby the agent learns the transition probabilities between states ans uses that to choose the best action, given the current state and it's belief about what the new state will be. 
#############################################################
